Report and analysis on implementation of IMM algorithm for multiple-model dynamics tracking

### 2020-02-02 Latex/draft.tex
Finished I guess

\section*{Introduction}
\justify
The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
multiple-model dynamics tracking as the tracked agent switches between linked models of movement by the means of a Markov chain. The goal 
is to evaluate the best trade-off between error on estimated position and real position and number of messages regarding consensus involved in the tracking.

@@

    \subsection*{Sensor's model}

@@

        &z(k)=h(x(k))+v(k)\\
        &\begin{bmatrix}
            \rho(k)\\ \theta (k)(k)

@@

            \sqrt{x_{1}(k)^2+x_{2}(k)^2}\\ atan2(x_{2}(1)/x_{1}(k))

@@

            v_{1}(k)\\v_{2}(k)

@@

            \sigma^{2}_{\rho}&0\\
            0&\sigma^{2}_{\theta (k)}

@@

            \frac{x_{1}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & \frac{x_{2}}{\sqrt{x_{1}^{2}+x_{2}^{2}}}& 0 \dots\\
            \frac{-x_{2}}{x_{1}^{2}+x_{2}^{2}}  & \frac{x_{1}}{x_{1}^{2}+x_{2}^{2}}& 0 \dots\\
        \end{bmatrix}_{|x(k)}

@@

    \section*{Model used}
    As mentioned already, the agent we want to track has a variable-model dynamic that can switch between different elements in a set 
    of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accellerated Walk $\mathbbm{M}_{1}$ 
    and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by a white 
    noise on their inputs.
    \subsection*{Random Accellerated Walk}
    For the Random Accellerated Walk we consider the set $\mathbbm{M}_{1}$ to be 5 elements large. 
    Here the elements are described
    \begin{center}
        \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
            \hline
             Random Walk  \\
            \hline\hline
             Mode & Behaviour  \\ [0.5ex]
            \hline\hline
            Mode 1 & Constant Speed \\
            \hline
            Mode 2  & Positive Acceleration in x  \\
            \hline
            Mode 3  & Negative Acceleration in x  \\
            \hline
            Mode 4  & Positive Acceleration in y  \\
            \hline
            Mode 5  & Negative Acceleration in y   \\ [1ex]
            \hline
        \end{tabular}
    \end{center}

@@

    where $A$ is the state matrix, $B(s_{k})$ the input matrix function of the mode/index $s_{k}$ that indicates the element picked of $\mathbbm{M}_{1}$, 

@@

            \sigma^{2}_{a_{x}}&0\\
            0&\sigma^{2}_{a_{y}}

@@

        p_{0}&p&p&p&p\\
        b&q_{0}&2q&q&2q\\
        b&2q&q_{0}&2q&q\\
        b&q&2q&q_{0}&2q\\
        b&2q&q&2q&q_{0}\\

@@

        \sigma^{2}_{\omega}&0\\
        0&\sigma^{2}_{\Omega}

@@

        p_{0}&p&p&p&p\\
        q&q_{0}&q&0&0\\
        q&q&q_{0}&0&0\\
        q&0&0&q_{0}&q\\
        q&0&0&q&q_{0}

@@

Being the agent's dynamic costantly switching between the models in the set chosen, a single kalman filter won't give us acceptable results while 

@@

@@

                &\mu^{(i)}_{k|k-1}=\sum_{j}\pi_{ji}\mu^{(j)}_{k-1}\\
                &\mu^{(j|i)}_{k-1}=\pi_{ji}\mu^{(j)}_{k-1}/\mu^{(i)}_{k|k-1}\\
                &\bar{x}^{(i)}_{k-1|k-1}=\sum_{j}\hat{x}^{(j)}_{k-1|k-1}\mu^{j|i}_{k-1}\\
                &\bar{P}^{(i)}_{k-1|k-1}=\sum_{j}[P^{(j)}_{k-1|k-1}+(\bar{x}^{(i)}_{k-1|k-1}\\
                &-\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})^{T}]\mu_{k-1}^{j|i}

@@

        transition matrix to then use the result to combine both the previous step state and covariance estimation.
     \item Model Conditioned filtering, in our case EKF $\forall m_{i}\in \mathbbm{M}$

@@

            &\hat{x}^{(i)}_{k|k-1}=f^{(i)}_{k}(\bar{x}^{(i)}_{k-1|k-1})\\
            &P^{(i)}_{k|k-1}=F^{(i)}_{k-1}\bar{P}^{(i)}_{k-1|k-1}F^{(i)^{T}}_{k-1}+G^{(i)}_{k-1}Q_{k-1}^{(i)}G^{(i)^{T}}_{k-1}\\
            &\bar{z}^{(i)}_{k}=z_{k}-h(\hat{x}^{(i)}_{k|k-1})\\
            &S^{(i)}_{k}=H^{(i)}_{k}P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}+R^{(i)}_{k}\\
            &W^{(i)}_{k}=P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}S^{(i)^{-1}}_{k}\\
            &\hat{x}^{(i)}_{k|k}=\hat{x}^{(i)}_{k|k-1}+W^{(i)}_{k}\bar{z}^{(i)}_{k}\\
            &P^{(i)}_{k|k}=P^{(i)}_{k|k-1}-W^{(i)}_{k}S^{(i)}_{k}W^{(i)^{T}}_{k}

@@

@@

            &L^{(i)}_{k}=\mathcal{N}(\bar{z}^{(i)}_{k},0,S^{(i)}_{k})\\
            &\mu^{(i)}_{k}=\frac{\mu^{(i)}_{k|k-1}L^{(i)}_{k}}{\sum_{j}\mu^{(j)}_{k|k-1}L^{(j)}_{k}}

@@

@@

         &\hat{x}_{k|k}=\sum_{i}x^{(i)}_{k|k}\mu^{(i)}_{k}\\
         &P_{k|k}=\sum_{i}[P^{(i)}_{k|k}+(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})^{T}]\mu_{k}^{i}

@@

@@

    Right having computed the IMM's estimate for every ON sensor, we use a consensus algorithm to try to lower the 

@@

        &P_{cons}(k)=(H^{k^{T}}P^{k^{-1}}H^{k})^{-1}\\
        &x_{cons}(k)=P_{cons}H^{k^{T}}P^{k^{-1}}Z^{k}

@@

@@

    \section*{Result}
    The performance evaluation of the system are evaluted by computing the RMS of the predicted trajectory eith the respect to the actual one
    choosing different rate of performind the WSL. The final result are listed in the table below
        \begin{tabular}{ |c||c|c|c|  }
            \multicolumn{4}{|c|}{consensus20} \\
            IMM  & Mean of Imm's mean    & Max of Imm's mean     & max of IMM's max  \\ [0.5ex]
            R1,Q1           & 0.1078                & 0.2578                & 0.3960                 \\
                R1,Q2           & 0.1094                & 0.2694             & 0.4671                      \\
                R2,Q1           & 0.0505                &  0.1210           & 0.2491                         \\
                R2,Q2           & 0.0514                & 0.1313             & 0.2549                   \\
            \multicolumn{4}{|c|}{consensus20} \\
            W/o Cons  & Mean of Imm's mean    & Max of Imm's mean     & max of IMM's max  \\ 
            R1,Q1           & 0.1609                & 0.1762                & 2.0937                 \\
            R1,Q2           & 0.1625                & 0.1907             & 1.0347                     \\
            R2,Q1           & 0.0799               &  0.0877           & 0.4310                         \\
            R2,Q2           & 0.0815                & 0.0926            & 0.4445                   \\

    \subsection*{}

>>>>

\section*{Introduction}
\justify
The purpouse of this project is to analyze and evaluate the performance of an IMM algorithm's implementation in a distributed environment for
multiple-model dynamics tracking. The tracked agent switches between linked models of movement by the means of a Markov chain. The goal
is to evaluate the best trade-off between error on estimated position and real position and number of messages regarding consensus involved in the tracking.

@@

\section*{Sensor's model}
\label{sensor}

@@

     & z(k)=h(x(k))+v(k)          \\
     & \begin{bmatrix}
        \rho(k) \\ \theta (k)(k)

@@

        \sqrt{x_{1}(k)^2+x_{2}(k)^2} \\ atan2(x_{2}(1)/x_{1}(k))

@@

        v_{1}(k) \\v_{2}(k)

@@

        \sigma^{2}_{\rho} & 0                       \\
        0                 & \sigma^{2}_{\theta (k)}

@@

        \frac{x_{1}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & \frac{x_{2}}{\sqrt{x_{1}^{2}+x_{2}^{2}}} & 0 \dots \\
        \frac{-x_{2}}{x_{1}^{2}+x_{2}^{2}}       & \frac{x_{1}}{x_{1}^{2}+x_{2}^{2}}        & 0 \dots \\
    \end{bmatrix}_{|x=x(k)}

@@

\section*{Model used}
As mentioned already, the agent we want to track has a variable-model dynamic that can switch between different elements in a set
of models that we denote as $\mathbbm{M}$. We will consider 2 families of such sets that we will call: Random Accelerated Walk $\mathbbm{M}_{1}$
and Random Unicycle Turning $\mathbbm{M}_{2}$. Every element of said families is a discrete Markovian process, as all are influenced by a white
noise on their inputs.
\subsection*{Random Accelerated Walk}
For the Random Accelerated Walk we consider the set $\mathbbm{M}_{1}$ to be 5 elements large.
Here the elements are described
\begin{center}
    \begin{tabular}{||c||c |c |}%{|width=\columnwidth|}
        \hline
        Random Walk                         \\
        \hline\hline
        Mode   & Behaviour                  \\ [0.5ex]
        \hline\hline
        Mode 1 & Constant Speed             \\
        \hline
        Mode 2 & Positive Acceleration in x \\
        \hline
        Mode 3 & Negative Acceleration in x \\
        \hline
        Mode 4 & Positive Acceleration in y \\
        \hline
        Mode 5 & Negative Acceleration in y \\ [1ex]
        \hline
    \end{tabular}
\end{center}

@@

where $A$ is the state matrix, $B(s_{k})$ the input matrix function of the mode/index $s_{k}$ that indicates the element picked of $\mathbbm{M}_{1}$ at timestep $k$,

@@

        \sigma^{2}_{a_{x}} & 0                  \\
        0                  & \sigma^{2}_{a_{y}}

@@

        p_{0} & p     & p     & p     & p     \\
        b     & q_{0} & 2q    & q     & 2q    \\
        b     & 2q    & q_{0} & 2q    & q     \\
        b     & q     & 2q    & q_{0} & 2q    \\
        b     & 2q    & q     & 2q    & q_{0} \\

@@

        \sigma^{2}_{\omega} & 0                   \\
        0                   & \sigma^{2}_{\Omega}

@@

        p_{0} & p     & p     & p     & p     \\
        q     & q_{0} & q     & 0     & 0     \\
        q     & q     & q_{0} & 0     & 0     \\
        q     & 0     & 0     & q_{0} & q     \\
        q     & 0     & 0     & q     & q_{0}

@@

Being the agent's dynamic costantly switching between the models in the set chosen, a single Kalman filter won't give us acceptable results while

@@

Following is a short recapof the algorithm, to see it in much more detail refer to %\cite%

@@

               & \mu^{(i)}_{k|k-1}=\sum_{j}\pi_{ji}\mu^{(j)}_{k-1}                                              \\
               & \mu^{(j|i)}_{k-1}=\pi_{ji}\mu^{(j)}_{k-1}/\mu^{(i)}_{k|k-1}                                    \\
               & \bar{x}^{(i)}_{k-1|k-1}=\sum_{j}\hat{x}^{(j)}_{k-1|k-1}\mu^{j|i}_{k-1}                         \\
               & \bar{P}^{(i)}_{k-1|k-1}=\sum_{j}[P^{(j)}_{k-1|k-1}+(\bar{x}^{(i)}_{k-1|k-1}                    \\
               & -\hat{x}^{(j)}_{k-1|k-1})(\bar{x}^{(i)}_{k-1|k-1}-\hat{x}^{(j)}_{k-1|k-1})^{T}]\mu_{k-1}^{j|i}

@@

          transition matrix to then use the result to combine both the previous step state and covariance estimation. It is to 
          notice that the transpose of the matrix formed by the collection of $\mu^{(j|i)}_{k-1}$ is stochastic, this makes sense
          since it works as a normalized transition matrix while computing $\bar{P}^{(i)}_{k-1|k-1}$ and $\bar{x}^{(i)}_{k-1|k-1}$.
    \item Model Conditioned filtering $\forall m_{i}\in \mathbbm{M}$

@@

               & \hat{x}^{(i)}_{k|k-1}=f^{(i)}_{k}(\bar{x}^{(i)}_{k-1|k-1},u)                                                        \\
               & P^{(i)}_{k|k-1}=F^{(i)}_{k-1}\bar{P}^{(i)}_{k-1|k-1}F^{(i)^{T}}_{k-1}+G^{(i)}_{k-1}Q_{k-1}^{(i)}G^{(i)^{T}}_{k-1} \\
               & \bar{z}^{(i)}_{k}=z_{k}-h(\hat{x}^{(i)}_{k|k-1})                                                                  \\
               & S^{(i)}_{k}=H^{(i)}_{k}P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}+R^{(i)}_{k}                                                 \\
               & W^{(i)}_{k}=P^{(i)}_{k|k-1}H^{(i)^{T}}_{k}S^{(i)^{-1}}_{k}                                                        \\
               & \hat{x}^{(i)}_{k|k}=\hat{x}^{(i)}_{k|k-1}+W^{(i)}_{k}\bar{z}^{(i)}_{k}                                            \\
               & P^{(i)}_{k|k}=P^{(i)}_{k|k-1}-W^{(i)}_{k}S^{(i)}_{k}W^{(i)^{T}}_{k}

@@

          This part of the algorithm is the one that includes all the estimation filters running in parallel. In the case 
          of $\mathbbm{M}_{1}$ we use a Kalman filter with a non-linear $h(x)$, so $f^{(i)}_{k}(x,u)$ is just the linear model 
          $(i)$ inside $\mathbbm{M}_{1}$ while $F^{(i)}_{k-1}$ is $A$ and $G^{(i)}_{k-1}$ is $G$ specified in the model. In 
          $\mathbbm{M}_{2}$ case an Extended Kalman Filter is used since $f^{(i)}_{k}(x,u)$ is non-linear for every model $(i)$, 
          so here $F^{(i)}_{k-1}$ is the Jacobian of the non-linear function without noise evaluated in $\bar{x}^{(i)}_{k-1|k-1},\ u$ while 
          $G^{(i)}_{k-1}$ is $\nabla_{w}f^{(i)}_{k}(x,u)$ evaluated in the same point with noise$=0$. Both power spectral density 
          matrices $Q$ and $R$ are constant by assumption. The matrix $H^{(i)}_{k}$ will be model $(i)$ agnostic, computed 
          as already discussed in section \ref{sensor} and evaluated in $\hat{x}^{(i)}_{k|k-1}$ (each different sensor will 
          calculate its relative position from that coordinate).

@@

               & L^{(i)}_{k}=\mathcal{N}(\bar{z}^{(i)}_{k},0,S^{(i)}_{k})                                \\
               & \mu^{(i)}_{k}=\frac{\mu^{(i)}_{k|k-1}L^{(i)}_{k}}{\sum_{j}\mu^{(j)}_{k|k-1}L^{(j)}_{k}}

@@

          Here we compute what is the actual probability of the model $m_{i}\in\mathbbm{M}$ to have guided the dynamic of 
          our agent at timestep $k$. To do so we assume that the the probability distribution of the error $\bar{z}_{k}$ should be 
          a Gaussian with $0$ mean and as covariance the innovation covariance $S^{(i)}_{k}$ given by the filter $(i)$ at timestep
           $k$, and we compute the $L^{(i)}_{k}$ probability density function in $\bar{z}^{(i)}_{k}$. Using this result we re-normalize the previously 
           computed $\mu^{(i)}_{k|k-1}$ to give us the output vector of model probabilities $\mu_{k}$.
           In this step a lower bound on the likelihood is implemented since a likelihood vector of $0$ breaks the algorithm.

@@

               & \hat{x}_{k|k}=\sum_{i}x^{(i)}_{k|k}\mu^{(i)}_{k}                                                                      \\
               & P_{k|k}=\sum_{i}[P^{(i)}_{k|k}+(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})(\hat{x}_{k|k}-\hat{x}^{(i)}_{k|k})^{T}]\mu_{k}^{i}

@@

          Using the vector $\mu_{k}$ computed at the previous step we mix all of the predictions computed by the filters to get 
          the outputs. This last step is only for the sake of the output, the algorithm forms a loop without it.

@@

Right after having computed the IMM's estimate for every ON sensor, we use a consensus algorithm to try to lower the

@@

     & P_{cons}(k)=(H^{k^{T}}P^{k^{-1}}H^{k})^{-1}  \\
     & x_{cons}(k)=P_{cons}H^{k^{T}}P^{k^{-1}}Z^{k}

@@

The consensus is computed both on the output of the IMM filter and all the outputs of its internal Kalman filters.

@@

\newpage
\section*{Results}
Here we present the results of our implementation of the algorithm and sensors. The agent was left wandering inside the set virtual room 
and measured at each timestep the estimation error that the algorithm gave. The room is set to be a square with a $100m$ side with a $10\times 10$ 
grid of sensors with range$=10$. 
The simulations were performed in a loop according to the Montecarlo's Method. We set a number of iterations for any specific case to 
$n_{monte}=100$ and each iteration stop wheter the agent leaves the room limits or a number of timesteps $n_{k}=1000$ is reached. The starting
 position and starting model are randomized at each iteration.
The performance indexes that we evaluated are:
    \item The Root Mean Square of the means of the errors at each Montecarlo's iteration
    \item The Root Mean Square of the maximum error at every Montecarlo's iteration
    \item The Maximum error between all Montecarlo's iterations
We evaluated both model sets $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$ for different consensus rate (how many timestep between each consensus), 
different $R$s and $Q$s and we considered both the errors given by the Consensus and by each individual sensor's IMM. 
The timestep $\delta$ is set at $0.05s$, the radius of the wheel $r$ at $0.5m$ while the inputs are
    u_{1}=\begin{bmatrix}
        5\frac{m}{s^{2}} \\5\frac{m}{s^{2}}
    \end{bmatrix}\ \ \ \ 
    u_{2}=\begin{bmatrix}
        3\frac{rad}{s^{2}} \\6\frac{rad}{s}
The power spectral density matrices considered are $R1=diag(0.1,(\frac{2\pi}{180})^{2})$ and $R2=diag(0.01,(\frac{2\pi}{360})^{2})$ for all the sensors, 
and while $Q2=diag(1,1)$ is shared by $\mathbbm{M}_{1}$ and $\mathbbm{M}_{2}$, $Q1=diag(0.2,0.2)$ for $\mathbbm{M}_{2}$ and $Q1=diag(0.1,0.1)$ for $\mathbbm{M}_{1}$.
The first case is $\mathbbm{M}_{1}$, the second $\mathbbm{M}_{2}$. Here are reported all the results of the simulations, all in meters.
%%%%%%%%%%%% SENSOR %%%%%%%%%%%%%%%%%%%

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{Sensor}                 \\
                \hline
                Measure & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1   & 0.3985        & 1.2407       & 1.7790      \\
                \hline
                % R1,Q2           & 0.1132                &  0.2847           & 0.6577                      \\
                % \hline
                R2,Q1   & 0.1574        & 0.5454       & 0.7139      \\
                % \hline
                % R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
                \hline
            \end{tabular} $}
\end{center}
This table is needed to compare the simulations results, because the power spectral density matrices $R$ regard the polar coordinates, while here
 we have the errors in cartesian. If the algorithm gives an error greater in all cases than what is given by the sensors, 
then it is useless.

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 1: consensus rate = 20}      \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1078        & 0.2578       & 0.3960      \\
                \hline
                R1,Q2     & 0.1094        & 0.2694       & 0.4671      \\
                \hline
                R2,Q1     & 0.0505        & 0.1210       & 0.2491      \\
                \hline
                R2,Q2     & 0.0514        & 0.1313       & 0.2549      \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.1609        & 0.1762       & 2.0937      \\
                \hline
                R1,Q2     & 0.1625        & 0.1907       & 1.0347      \\
                \hline
                R2,Q1     & 0.0799        & 0.0877       & 0.4310      \\
                \hline
                R2,Q2     & 0.0815        & 0.0926       & 0.4445      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%% rate 10 %%%%%

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 1: consensus rate = 10}      \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1110        & 0.2831       & 0.4460      \\
                \hline
                R1,Q2     & 0.1129        & 0.2940       & 0.5227      \\
                \hline
                R2,Q1     & 0.0516        & 0.1406       & 0.2226      \\
                \hline
                R2,Q2     & 0.0519        & 0.1331       & 0.2429      \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.1455        & 0.1678       & 0.9         \\
                \hline
                R1,Q2     & 0.1478        & 0.1926       & 1.5835      \\
                \hline
                R2,Q1     & 0.0751        & 0.0853       & 0.4441      \\
                \hline
                R2,Q2     & 0.0756        & 0.0824       & 0.4522      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%% rate 5 %%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 1: consensus rate = 5}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1158        & 0.3516       & 1.2838      \\
                \hline
                R1,Q2     & 0.1192        & 0.3245       & 0.5018      \\
                \hline
                R2,Q1     & 0.0553        & 0.1649       & 0.3532      \\
                \hline
                R2,Q2     & 0.0542        & 0.1649       & 0.2246      \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.1302        & 0.2460       & 1.808       \\
                \hline
                R1,Q2     & 0.1359        & 0.1700       & 1.7787      \\
                \hline
                R2,Q1     & 0.0666        & 0.0762       & 0.762       \\
                \hline
                R2,Q2     & 0.0661        & 0.0738       & 0.4450      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%% rate 2 %%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 1: consensus rate = 2}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1158        & 0.3516       & 1.2838      \\
                \hline
                % R1,Q2           & 0.1094                & 0.2694             & 0.4671                      \\
                % \hline
                R2,Q1     & 0.0598        & 0.1925       & 0.2654      \\
                % \hline
                % R2,Q2           & 0.0514                & 0.1313             & 0.2549                   \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.1320        & 0.2460       & 1.808       \\
                \hline
                % R1,Q2           & 0.1625                & 0.1907             & 1.0347                     \\
                % \hline
                R2,Q1     & 0.0617        & 0.0741       & 0.4368      \\
                % \hline
                % R2,Q2           & 0.0815                & 0.0926            & 0.4445                   \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%% rate 1 %%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 1: consensus rate = 1}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.4265        & 1.6287       & 4.5672      \\
                \hline
                % R1,Q2         & 0.0757                & 0.204             & 0.2612                        \\
                % \hline
                R2,Q1     & 0.0757        & 0.204        & 0.2612      \\
                % \hline
                % R2,Q2           & 0.0514                & 0.1313             & 0.2549                   \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.3755        & 0.8706       & 5.9070      \\
                % \hline
                % R1,Q2           & 0.1625                & 0.1907             & 1.0347                     \\
                \hline
                R2,Q1     & 0.0766        & 0.1128       & 0.4872      \\
                % \hline
                % R2,Q2           & 0.0815                & 0.0926            & 0.4445                   \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%% no cons %%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 1: consensus rate = 2}      \\
                \hline
                Individual IMM & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1    & 0.1790        & 0.2278       & 1.7442      \\
                \hline
                R1,Q2    & 0.1800        & 0.2782       & 6.4459      \\
                \hline
                R2,Q1    & 0.3961        & 0.0930       & 0.0850      \\
                \hline
                R2,Q2    & 0.0864        & 0.0973       & 0.7242      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%%%%%%%%%%%%%%%%% 20 %%%%%%%%%%%%%%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: consensus rate = 20}      \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1167        & 0.3027       & 0.7750      \\
                \hline
                R1,Q2     & 0.1132        & 0.2847       & 0.6577      \\
                \hline
                R2,Q1     & 0.0512        & 0.1325       & 0.2315      \\
                \hline
                R2,Q2     & 0.0539        & 0.1454       & 0.2334      \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.0771        & 0.0903       & 0.4918      \\
                \hline
                R1,Q2     & 0.1664        & 0.2726       & 1.0990      \\
                \hline
                R2,Q1     & 0.0771        & 0.0903       & 0.4918      \\
                \hline
                R2,Q2     & 0.0804        & 0.0947       & 0.4190      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%%%%%%%%%%%% 10 %%%%%%%%%%%%%%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: consensus rate = 10}      \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1228        & 0.3438       & 0.5992      \\
                \hline
                R1,Q2     & 0.1214        & 0.3291       & 0.7441      \\
                \hline
                R2,Q1     & 0.0535        & 0.1536       & 0.2525      \\
                \hline
                R2,Q2     & 0.0539        & 0.1439       & 0.2396      \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.1566        & 0.1938       & 0.8766      \\
                \hline
                R1,Q2     & 0.1577        & 0.2278       & 1.4168      \\
                \hline
                R2,Q1     & 0.0742        & 0.0906       & 0.3968      \\
                \hline
                R2,Q2     & 0.0759        & 0.0935       & 0.4782      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% 555555 %%%%%%%%%%%%%%%%
\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: consensus rate = 5}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.1984        & 0.7467       & 2.3522      \\
                \hline
                R1,Q2     & 0.1925        & 0.5871       & 2.2983      \\
                \hline
                R2,Q1     & 0.0604        & 0.1829       & 0.4389      \\
                \hline
                R2,Q2     & 0.0628        & 0.1873       & 0.2912      \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.2135        & 0.7295       & 2.4394      \\
                \hline
                R1,Q2     & 0.2116        & 0.5412       & 2.7371      \\
                \hline
                R2,Q1     & 0.0722        & 0.1012       & 0.4599      \\
                \hline
                R2,Q2     & 0.0742        & 0.1077       & 0.5699      \\
                \hline
            \end{tabular} $}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%       2          %%%%%%%%%%%%%%%%%%%%

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: consensus rate = 2}       \\
                \hline
                Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\ [0.5ex]
                \hline
                R1,Q1     & 0.6709        & 3.2770       & 8.4954      \\
                \hline
                % R1,Q2           & 0.1132                &  0.2847           & 0.6577                      \\
                % \hline
                R2,Q1     & 0.1392        & 0.6907       & 2.0562      \\
                % \hline
                % R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
                \hline
                \multicolumn{4}{|c|}{}                                 \\
                \hline
                Individual IMM  & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1     & 0.07629       & 2.5799       & 9.3296      \\
                % \hline
                % R1,Q2        & 0.1664                & 0.2726                & 1.0990              \\
                \hline
                R2,Q1     & 0.1585        & 0.5868       & 2.1211      \\
                %     \hline
                %     R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
                % \hline
            \end{tabular} $}
\end{center}

%%%%%%%%%%%%%%%%%%%% 1 1 1 %%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
    \begin{tabular}{ |c||c|c|c|  }
        \hline
        \multicolumn{4}{|c|}{case 2: consensus rate = 1} \\
        \hline
        Consensus & RMS of Means & RMS of Maxes & Max of Maxes \\  [0.5ex]
        \hline
        R1,Q1    &      1.3654 & 5.5341 & 16.2066             \\
            \hline
             R2,Q1            & 0.3883                & 2.3273               & 5.1490                      \\
             \hline
        %     R2,Q1            & 0.0512                & 0.1325             & 0.2315                      \\
        %     \hline
        %     R2,Q2           & 0.0539                & 0.1454             & 0.2334                   \\
        % \hline
        \multicolumn{4}{|c|}{} \\
        \hline
        Individual IMM & RMS of Means & RMS of Maxes & Max of Maxes \\ 
        \hline
        R1,Q1      & 1.4520 & 5.6335 & 16.4740          \\
         \hline
        % R1,Q2        & 0.1664                & 0.2726                & 1.0990              \\
        % \hline
         R2,Q1         & 0.3867                & 1.3242             & 5.3175                         \\
        \hline
        % R2,Q2           & 0.0804                & 0.0947            & 0.4190                   \\
    \hline
       \end{tabular} $}
    \end{center}

%%%%% NO cons %%%%%%%%%%%%%%%%

\begin{center}
    \resizebox{.99 \columnwidth}{!}{ $
            \begin{tabular}{ |c||c|c|c|  }
                \hline
                \multicolumn{4}{|c|}{case 2: no consensus}                             \\
                \hline
                Individual IMM & RMS of Means & RMS of Maxes & Max of Maxes \\
                \hline
                R1,Q1    & 0.1784        & 0.2516       & 1.5541      \\
                \hline
                R1,Q2    & 0.1795        & 0.2145       & 0.9872      \\
                \hline
                R2,Q1    & 0.0845        & 0.0962       & 0.6888      \\
                \hline
                R2,Q2    & 0.0843        & 0.1090       & 0.9289      \\
                \hline
            \end{tabular} $}
\end{center}
